---
title: "Data Reanalysis of Wang et al. (2018)"
author: "Kevin Sanchez"
date: "4/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = TRUE,
	message = TRUE,
	comment = "##",
	prompt = FALSE,
	tidy = TRUE,
	tidy.opts = list(blank = FALSE, width.cutoff = 75),
	fig.path = "img/",
	fig.align = "center"
)
```

## Introduction

### Wang et al. (2018) — 17β-estradiol (E2) promotes growth and stability of new dendritic spines via estrogen receptor β pathway in intact mouse cortex

Recent studies have found that altering levels of estradiol (E2), the most potent estrogen,
can affect neuronal function in several brain regions like the hippocampus and prefrontal
cortex. One potential mechanism is through modulation of dendritic spine density in these 
brain regions, which can impact advanced cognitive functions like learning and memory. 
The objective of this paper is to quantify how E2 treatment can alter the growth and removal 
of these dendritic spines. Additionally, the authors wanted to investigate which of the two 
estrogen receptors (ERs), ERα and ERβ, are involved in mediating this process. They used the
ER agonists α-PPT and β-DPN to enhance the activity of ERα and ERβ, respectively.

Their raw data is stratified into two discrete time periods where they observed changes in 
dendritic spines: 0-4 days (d4) and 4-8 days (d8). For some analyses, they used the
combination of these time periods from 0-8 days (dT). The raw data quantifies the total 
number of dendritic spines initially observed (d#_total) and the number of spines that were 
stable, eliminated, or formed after the time period described (d#_stable, d#_elim, d#_form, 
respectively).

The analyses performed by the authors include descriptive statistics for each of the 
parameters described above, including the mean, standard deviation, and standard
error of the mean. To determine if there were differences between experimental groups, 
the authors employed a t-test. All of their data were graphed as bar graphs.

In this assignment, I will be replicating all of the descriptive statistics that the 
authors performed. Using their data comparing dendritic spine characteristics between the
control and E2-treated mice, I will redo their t-test and compare it to the authors's
results. Lastly, I will recreate the three graphs from Figure 2 of their paper.

## Visualization of Data
```{r}
library(readxl)
file <- ""
rawdata <- read_excel(file, sheet = 1, col_names = TRUE)
```

## Replications and Reanalysis

## Discussion

## References